---
title: "RWorksheet_Esmalla#4a.Rmd"
author: "Janessa Marie Esmalla"
date: "2023-10-25"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```

```{r name, echo = TRUE} 

shoesize_vec <- c(6.5,9.0,8.5,10.0,7.0,9.5,9.0,13.0,7.5,10.5,8.5,12.5,10.5,13.5,11.5,8.5,10.5,6.5,7.5,8.5,10.5,11.0,9.0,13.0)
height_vec <- c (66.0,68.0,64.5,65.0,70.0,64.0,70.0,71.0,72.0,64.0,74.5,67.0,71.0,71.0,77.0,72.0)
gender_vec <- c()

HouseholdData <- data.frame(
  shoe_size = shoesize_vec,
  height = height_vec,
  gender = gender_vec
 )
 


months_vector <- c("March", "April", "January", "November", "January", "September", "October", "September", "November", "August", "January", "November", "November", "February", "May", "August", "July", "December", "August", "August", "September", "November", "February", "April")

factor_months_vector <- factor(months_vector)

# Print the factor_months_vector
print(factor_months_vector)

summary(months_vector)
summary(factor_months_vector)

direction_data <- c("East", "West", "North")
frequency_data <- c(1, 4, 3)

factor_data <- factor(direction_data, levels = c("East", "West", "North"))
print(factor_data)




  


# Generate a random number between 1 and 50
selected_number <- sample(1:50, 1)

# User input for a number
user_input <- as.integer(readline("Enter a number between 1 and 50: "))

# Check if the user input is within the specified range
if (user_input < 1 || user_input > 50) {
  cat("The number selected is beyond the range of 1 to 50\n")
} else if (user_input == 20) {
  cat("TRUE\n")
} else {
  cat(user_input, "\n")
}

# Function to calculate the minimum number of bills needed
calculate_minimum_bills <- function(price) {
  # Define the available bill denominations
  bill_denominations <- c(1000, 500, 200, 100, 50)
  
  # Initialize a variable to keep track of the total number of bills
  total_bills <- 0
  
  # Iterate through each bill denomination
  for (bill in bill_denominations) {
    # Calculate how many of these bills can be used for the given price
    num_bills <- floor(price / bill)
    if (num_bills > 0) {
      # Update the total number of bills and reduce the price accordingly
      total_bills <- total_bills + num_bills
      price <- price - (num_bills * bill)
    }
  }
  
  # Print the minimum number of bills needed
  cat("Minimum number of bills needed:", total_bills, "\n")
}

# Example usage:
price <- 750  # Replace this with the price of the snack (must be divisible by 50)
calculate_minimum_bills(price)


