---
title: "RWorksheet_Esmalla3a"
author: "Janessa Marie Esmalla"
date: "2023-10-07"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r name, echo = TRUE} 

# 1.There is a built-in vector LETTERS contains the uppercase letters of the alphabet and letters which contains the lowercase letters of the alphabet.

# 1a. You need to produce a vector that contains the first 11 letters.
first_11_letters <- LETTERS[1:11]
first_11_letters

# 1b. Produce a vector that contains the odd numbered letters.
odd_numbered_letters <- LETTERS[seq(1, length(LETTERS), by = 2)]
odd_numbered_letters

# 1c. Produce a vector that contains the vowels
vowels <- LETTERS[LETTERS %in% c("A", "E", "I", "O", "U")]
vowels


# Based on the above vector letters:

lower_Alphabet <- letters[1:26]
lower_Alphabet

# 1d. Produce a vector that contains the last 5 lowercase letters.
last_five_let <- letters[22:26]
last_five_let

# 1e. Produce a vector that contains letters between 15 to 24 letters in lowercase.
letters_15_to_24 <- letters[15:24]
letters_15_to_24

# 2. Create a vector(not a dataframe) with the average temperatures in April for Tugue-garao City, Manila, Iloilo City, Tacloban, Samal Island, and Davao City. The average temperatures in Celcius are 42, 39, 34, 34, 30, and 27 degrees.

# 2a. What is the R code and its result for creating a character vector for the city/town of Tuguegarao City, Manila, Iloilo City, Tacloban,Samal Island, and Davao City? Name the object as city. The names should follow the same order as in the instruction 
city <- c("Tuguegarao City", "Manila", "Iloilo City", "Tacloban", "Samal Island", "Davao City")
city

# 2b. The average temperatures in Celcius are 42, 39, 34, 34, 30, and 27 degrees.Name the object as temp.
temp <- c(42, 39, 34, 34, 30, 27)
temp

# 2c. Create a dataframe to combine the city and the temp by using ‘data.frame(). What the R code and its result?
data_temp <- data.frame(City = city, Temperature = temp)
data_temp

# 2d. Associate the dataframe you have created in 2.(c) by naming the columns using the names() function. Change the column names by using names() function as City and Temperature.
names(data_temp) <- c("City", "Temperature")
names(data_temp)

# 2e. Print the structure by using str() function. Describe the output.
str(data_temp)

# 2f. From the answer in d, what is the content of row 3 and row 4 What is its R code and its output?
row_temp <- data_temp[3:4, ]
row_temp

# City with the highest temperature
max_temp_city <- data_temp[data_temp$Temperature == max(data_temp$Temperature), "City"]
max_temp_city

# City with the lowest temperature
min_temp_city <- data_temp[data_temp$Temperature == min(data_temp$Temperature), "City"]
min_temp_city



# USING MATRIX

# 3a.
mat <- matrix(c(1:8, 11:14), nrow = 3, ncol = 4)
mat

# 3b.
mat * 2
mat

# 3c.
mat[2, ]
mat

# 3d
mat[1:2, 3:4]
mat

# 3e.
mat[3, 2:3]
mat

# 3f.
mat[, 4]
mat

# 3g.
rownames(mat) <- c("isa", "dalawa", "tatlo")
rownames(mat)

colnames(mat) <- c("uno", "dos", "tres", "quatro")
colnames(mat)


dim(mat) <- c(6, 2)
mat


# USING ARRAYS

# 4 An array contains 1, 2, 3, 6, 7, 8, 9, 0, 3, 4, 5, 1
my_array <- c(1, 2, 3, 6, 7, 8, 9, 0, 3, 4, 5, 1)
my_array

# 4a.
new_array <- array(my_array , dim = c(2, 4 ,3))
new_array

# 4b.
dim(new_array)

# 4c.
colnames(new_array) <- c("A","B","C","D")
new_array

rownames(new_array) <- c("a","b")
new_array

dimnames(new_array)[[3]] <- c("1st-Dimensional Array", "2nd-Dimensional Array", "3rd-Dimensional Array")
new_array
