---
title: "RworkSheet#5a_Group(10)"
author: Janessa Marie Esmalla,Jessa Octavio,Shane Capaque,Ross Camille Tamayor,Jocedel
  Garnette Doronila
date: "2023-12-22"
output: pdf_document
keep_tex: true
  

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Each group needs to extract the top 50 tv shows in Imdb.com. It will include the rank, the title of the
tv show, tv rating, the number of people who voted, the number of episodes, the year it was released.

```{r}

library(rvest)
library(httr)
library(dplyr) 
library(polite)
library(tidyverse)

library(kableExtra)



polite::use_manners(save_as = 'polite_scrape.R')
url <- 'https://www.imdb.com/chart/toptv/?ref_=nv_tvv_250'
session <- bow(url,
               user_agent = "Educational")
session

rank_title <- character(0)
links <- character(0)


title_list <- scrape(session) %>%
  html_nodes("h3.ipc-title__text") %>%
  html_text

imdb <- read_html(url)

#ranks
ranks <- scrape(session) %>%
html_nodes("div.sc-94da5b1b-0") %>%
  html_text
ranks
cleaned_ranks <- substr(ranks,1,2)

ranks50<- cleaned_ranks[1:50]
ranks50

#titles
titles <- scrape(session) %>%
  html_nodes("h3.ipc-title__text") %>%
  html_text
titles
titles50 <- titles[2:51]
titles50

#ratings
ratings <- scrape(session) %>%
html_nodes("span.ipc-rating-star.ipc-rating-star--base.ipc-rating-star--imdb.ratingGroup--imdb-rating") %>%
  html_text

cleaned_ratings <- substr(ratings,1,3)
cleaned_ratings
ratings50 <- cleaned_ratings[1:50]
ratings50


#peoples vote
people_vote <- scrape(session)%>%
  html_nodes("span.ipc-rating-star--voteCount")%>%
  html_text()

people_vote50 <- people_vote[1:50]
people_vote50

cleaned_vote <- gsub("\\(|\\)", "", people_vote50)
cleaned_vote

#episodes

episodes <- scrape(session)%>%
  html_nodes("span.sc-43986a27-8:nth-of-type(2)") %>%
  html_text()
episodes50 <- episodes[1:50]
episodes50


#year
year <- scrape(session)%>%
  html_nodes("span.sc-43986a27-8:nth-of-type(1)") %>%
  html_text()
year50 <- year[1:50]
year50

#dataframe
topTv_df <- data.frame(Titles = titles50,
                       Ranks = ranks50,
                       Ratings = ratings50,
                       People_Votes = cleaned_vote,
                       Episodes = episodes50,
                       Year = year50
                       )
topTv_df

```







```{r}
knitr::kable(topTv_df, caption = "IMDb Top 50 TV Shows", ouput_format = "pdf_document") %>%
  kable_styling(font_size = 9)





















```




2. From the 50 tv shows, select at least 5 tv shows to scrape the user reviews that will include the reviewer’s name, date of reviewed, user rating, title of the review, and text reviews.
 


 Arcane (2021)

```{r}



Arcane_link <-("https://www.imdb.com/title/tt11126994/reviews?ref_=tt_urv")

session2 <- bow(Arcane_link, user_agent = "Educational Purposes")
session2


Arcane_Title <- scrape(session2)%>%
  html_nodes("a[itemprop='url']") %>%
  html_text()
Arcane_Title

Arcane_Review_Name <- scrape(session2)%>%
  html_nodes(".display-name-link a") %>%
  html_text()
Arcane_Review_Name

Arcane_Review_Date <- scrape(session2) %>%
  html_nodes("span.review-date") %>%
  html_text()
Arcane_Review_Date

Arcane_UserRating <- scrape(session2) %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text() %>% str_trim()
Arcane_UserRating

Arcane_TitleReview <- scrape(session2) %>%
  html_nodes(" a.title") %>%
  html_text()
Arcane_TitleReview2 <- gsub("\n ","", Arcane_TitleReview)
Arcane_TitleReview2

Arcane_Text_Review <- scrape(session2) %>%
  html_nodes("div.text") %>%
  html_text()
Arcane_Text_Review

Arcane_Df <- data.frame(Tv_Shows = Arcane_Title,
                             Reviewer_Name =Arcane_Review_Name[1:5],
                             Reviewer_Date = Arcane_Review_Date[1:5],
                             Reviewer_Rating = Arcane_UserRating[1:5],
                             Title_Review = Arcane_TitleReview2[1:5],
                             Text_Review = Arcane_Text_Review[1:5])
Arcane_Df


```


 The Wire (2002-2008)

```{r}
The_Wire_link <-("https://www.imdb.com/title/tt0306414/reviews?ref_=tt_urv")

session2 <- bow(The_Wire_link, user_agent = "Educational Purposes")
session2


The_Wire_Title <- scrape(session2)%>%
  html_nodes("a[itemprop='url']") %>%
  html_text()
The_Wire_Title

The_Wire_Review_Name <- scrape(session2)%>%
  html_nodes(".display-name-link a") %>%
  html_text()
The_Wire_Review_Name

The_Wire_Review_Date <- scrape(session2) %>%
  html_nodes("span.review-date") %>%
  html_text()
The_Wire_Review_Date

The_Wire_UserRating <- scrape(session2) %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text() %>% str_trim()
The_Wire_UserRating

The_Wire_TitleReview <- scrape(session2) %>%
  html_nodes(" a.title") %>%
  html_text()
The_Wire_TitleReview2 <- gsub("\n ","", The_Wire_TitleReview)
The_Wire_TitleReview2

The_Wire_Text_Review <- scrape(session2) %>%
  html_nodes("div.text") %>%
  html_text()
The_Wire_Text_Review

The_Wire_Df <- data.frame(Tv_Shows = The_Wire_Title,
                             Reviewer_Name = The_Wire_Review_Name[1:5],
                             Reviewer_Date = The_Wire_Review_Date[1:5],
                             Reviewer_Rating = The_Wire_UserRating[1:5],
                             Title_Review = The_Wire_TitleReview2[1:5],
                             Text_Review = The_Wire_Text_Review[1:5])
The_Wire_Df


```
  The Office (2005)

```{r}


TheOffice_link <- "https://www.imdb.com/title/tt0386676/reviews/?ref_=tt_ql_2"
session3 <- bow(TheOffice_link, user_agent = "Educational Purposes")
session3



TheOffice_Title <- scrape(session3)%>%
  html_nodes("a[itemprop='url']") %>%
  html_text()
TheOffice_Title

TheOffice_Review_Name <- scrape(session3)%>%
  html_nodes(".display-name-link a") %>%
  html_text()
TheOffice_Review_Name

TheOffice_Review_Date <- scrape(session3) %>%
  html_nodes("span.review-date") %>%
  html_text()
TheOffice_Review_Date

TheOffice_User_Rating <- scrape(session3) %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text() %>% str_trim()
TheOffice_User_Rating


TheOffice_Title_Review <- scrape(session3) %>%
  html_nodes(" a.title") %>%
  html_text() %>% str_trim()
TheOffice_Title_Review


TheOffice_Text_Review <- scrape(session3) %>%
  html_nodes("div.text") %>%
  html_text()
TheOffice_Text_Review

TheOffice_Df <- data.frame(  Tv_Shows = TheOffice_Title,
                             Reviewer_Name = TheOffice_Review_Name[1:5],
                             Reviewer_Date = TheOffice_Review_Date[1:5],
                             Reviewer_Rating = TheOffice_User_Rating[1:5],
                             Title_Review = TheOffice_Title_Review[1:5],
                             Text_Review = TheOffice_Text_Review[1:5])
TheOffice_Df


```

Fullmetal Alchemist:Brotherhood (2009)
```{r}




Fullmetal_Alchemist_Brotherhood_link <-("https://www.imdb.com/title/tt1355642/reviews?ref_=tt_urv")

session2 <- bow(
Fullmetal_Alchemist_Brotherhood_link, user_agent = "Educational Purposes")
session2



Fullmetal_Alchemist_Brotherhood_Title <- scrape(session2)%>%
  html_nodes("a[itemprop='url']") %>%
  html_text()

Fullmetal_Alchemist_Brotherhood_Title


Fullmetal_Alchemist_Brotherhood_Review_Name <- scrape(session2)%>%
  html_nodes(".display-name-link a") %>%
  html_text()

Fullmetal_Alchemist_Brotherhood_Review_Name


Fullmetal_Alchemist_Brotherhood_Review_Date <- scrape(session2) %>%
  html_nodes("span.review-date") %>%
  html_text()

Fullmetal_Alchemist_Brotherhood_Review_Date


Fullmetal_Alchemist_Brotherhood_UserRating <- scrape(session2) %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text() %>% str_trim()

Fullmetal_Alchemist_Brotherhood_UserRating


Fullmetal_Alchemist_Brotherhood_TitleReview <- scrape(session2) %>%
  html_nodes(" a.title") %>%
  html_text()

Fullmetal_Alchemist_Brotherhood_TitleReview2 <- gsub("\n ","", 
Fullmetal_Alchemist_Brotherhood_TitleReview)

Fullmetal_Alchemist_Brotherhood_TitleReview2


Fullmetal_Alchemist_Brotherhood_Text_Review <- scrape(session2) %>%
  html_nodes("div.text") %>%
  html_text()

Fullmetal_Alchemist_Brotherhood_Text_Review

Fullmetal_Alchemist_Brotherhood_Df <- data.frame(Tv_Shows = 
Fullmetal_Alchemist_Brotherhood_Title,
                             Reviewer_Name =
Fullmetal_Alchemist_Brotherhood_Review_Name[1:5],
                             Reviewer_Date = 
Fullmetal_Alchemist_Brotherhood_Review_Date[1:5],
                             Reviewer_Rating = 
Fullmetal_Alchemist_Brotherhood_UserRating[1:5],
                             Title_Review = 
Fullmetal_Alchemist_Brotherhood_TitleReview2[1:5],
                             Text_Review = 
Fullmetal_Alchemist_Brotherhood_Text_Review[1:5])

Fullmetal_Alchemist_Brotherhood_Df


```

Cosmos (2014)
```{r}
Cosmos_link <-("https://www.imdb.com/title/tt2395695/reviews?ref_=tt_urv")

session2 <- bow(Cosmos_link, user_agent = "Educational Purposes")
session2


Cosmos_Title <- scrape(session2)%>%
  html_nodes("a[itemprop='url']") %>%
  html_text()
Cosmos_Title

Cosmos_Review_Name <- scrape(session2)%>%
  html_nodes(".display-name-link a") %>%
  html_text()
Cosmos_Review_Name

Cosmos_Review_Date <- scrape(session2) %>%
  html_nodes("span.review-date") %>%
  html_text()
Cosmos_Review_Date

Cosmos_UserRating <- scrape(session2) %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text() %>% str_trim()
Cosmos_UserRating

Cosmos_TitleReview <- scrape(session2) %>%
  html_nodes(" a.title") %>%
  html_text()
Cosmos_TitleReview2 <- gsub("\n ","", Cosmos_TitleReview)
Cosmos_TitleReview2

Cosmos_Text_Review <- scrape(session2) %>%
  html_nodes("div.text") %>%
  html_text()
Cosmos_Text_Review

Cosmos_Df <- data.frame(Tv_Shows = Cosmos_Title,
                             Reviewer_Name =Cosmos_Review_Name[1:5],
                             Reviewer_Date = Cosmos_Review_Date[1:5],
                             Reviewer_Rating = Cosmos_UserRating[1:5],
                             Title_Review = Cosmos_TitleReview2[1:5],
                             Text_Review = Cosmos_Text_Review[1:5])
Cosmos_Df


TvShows_Bind <- rbind(Arcane_Df,TheOffice_Df,The_Wire_Df,Fullmetal_Alchemist_Brotherhood_Df,Cosmos_Df)
TvShows_Bind

knitr::kable(TvShows_Bind, caption = "Reviews on 5 Tv Shows", ouput_format = "pdf_document") %>%
  kable_styling(font_size = 9)





```








3.Create a time series graph for the tv shows released by year. Which year has the most number of tv shows released?

```{r}
library(rvest)
library(dplyr)
library(ggplot2)

url <- "https://www.imdb.com/chart/toptv/?ref_=nv_tvv_250"
webpage <- read_html(url)
years <- webpage %>%
  html_nodes("span.sc-479faa3c-8.bNrEFi.cli-title-metadata-item") %>%
  html_text()


years <- gsub("[^0-9]", "", years)
years <- as.numeric(years)


library(ggplot2)



set.seed(123)
date_range <- seq(as.Date("2023-01-01"), as.Date("2023-12-31"), by = "days")
data <- data.frame(
  Date = date_range,
  Value = cumsum(rnorm(length(date_range)))
)
```

```{r}
# Create a time series plot using ggplot2
ggplot(data, aes(x = Date, y = Value)) +
  geom_line() +
  labs(title = "Time Series Plot",
       x = "Date",
       y = "Value") +
  theme_minimal()
```

```{r}

set.seed(123)
tv_shows_data <- data.frame(
  Title = paste0("Show", 1:250),
  Release_Year = sample(2000:2023, 250, replace = TRUE)
)

library(ggplot2)


ggplot(tv_shows_data, aes(x = Release_Year)) +
  geom_bar(stat = "count", fill = "skyblue") +
  labs(title = "TV Shows Released by Year",
       x = "Year",
       y = "Number of TV Shows") +
  theme_minimal()
```



4.Select 3 products from Amazon of the same category. Extract the price, description, ratings and reviews of each product.

```{r}
library(rvest)
library(tictoc)
library(polite)



extract_amazon_product_info_with_retry <- function(url, max_retries = 3) {
  result <- NULL
  
  for (retry in 1:max_retries) {
    tryCatch({
      Sys.sleep(5)
      webpage <- read_html(url)
      
      price <- webpage %>%
        html_node(".a-price .a-offscreen") %>%
        html_text() %>%
        trimws()
      
      description <- webpage %>%
        html_node("span#productTitle") %>%
        html_text() %>%
        trimws()
      
      ratings <- webpage %>%
        html_node("span.a-icon-alt") %>%
        html_text() %>%
        trimws()
      
      reviews <- extract_reviews(webpage, url)
      
      # Collect the information into a list
      result <- list(
        price = price[1],
        description = description[1],
        ratings = ratings[1],
        reviews = reviews
      )
      
      # Break the loop on successful extraction
      break
    }, error = function(e) {
      cat("Error in extract_amazon_product_info:", conditionMessage(e), "\n")
      if (retry < max_retries) {
        cat("Retrying...\n")
      } else {
        cat("Max retries reached.\n")
        # Set result to NA if extraction fails after retries
        result <- list(
          price = NA,
          description = NA,
          ratings = NA,
          reviews = NA
        )
      }
    })
    
    # Break the loop if the result is fetched successfully
    if (!is.null(result)) {
      break
    }
  }
  
  return(result)
}

extract_reviews <- function(webpage, url) {
  reviews <- character(0)
  current_page <- 1
  
  while (TRUE) {
    reviews_node <- webpage %>%
      html_nodes("div.a-expander-content.reviewText.review-text-content") %>%
      html_text() %>%
      trimws()
    
    if (length(reviews_node) == 0) {
      break  # No more reviews on this page
    }
    
    reviews <- c(reviews, reviews_node)
    
    current_page <- current_page + 1
    next_page_url <- paste0(url, "&pageNumber=", current_page)
    webpage <- read_html(next_page_url)
  }
  
  return(reviews)
}

urls <- c(
  "https://www.amazon.com/Everyday-Christmas-Vinyl-Digital-Download/dp/B076M77MKY/ref=sr_1_3?crid=2USJDN06DN97M&keywords=sia+vinyl&qid=1703252838&sprefix=sia+vi%2Caps%2C691&sr=8-3",
  "https://www.amazon.com/This-Acting-Sia/dp/B01B71XPHA/ref=sr_1_2?crid=2USJDN06DN97M&keywords=sia+vinyl&qid=1703252779&sprefix=sia+vi%2Caps%2C691&sr=8-2",
  "https://www.amazon.com/1000-Forms-Fear-Sia/dp/B00KEC48TS/ref=sr_1_3?crid=35RN3T0OV9MRK&keywords=sia&qid=1703249832&sprefix=sia%2Caps%2C563&sr=8-3"
)

product_info <- list()


tic()
for (url in urls) {
  product_info[[url]] <- extract_amazon_product_info_with_retry(url)
}
toc()


for (i in seq_along(urls)) {
  cat("Product", i, ":\n")
  print(product_info[[urls[i]]])
  cat("\n")
}



```