---
title: "Rworksheet_Esmalla#4c"
author: "Janessa Marie Esmalla"
date: "2023-11-22"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

 1a. Show your solutions on how to import a csv file into the environment. 

```{r} 
 library(readr) 
 mpg_file <- read_csv("mpg.csv") 
 mpg_file
```

 1b.Which variables from mpg dataset are categorical? -->
```{r}

 str(mpg_file) 
categorical_vars <- c("manufacturer", "model", "year", "cyl", "trans", "drv", "fl", "class")
cat("Categorical variables:", categorical_vars, "\n")
``` 

1c. Which are continuous variables? 
```{r} 
 str(mpg_file) 
continuous_vars <- c("displ", "cty", "hwy")
cat("Continuous variables:", continuous_vars, "\n")
``` 

2. Which manufacturer has the most models in this data set? Which model has the most variations? 
 Show your answer.
```{r} 
 manufacturer_asTable <- table(mpg_file$manufacturer) 
names(manufacturer_asTable)[which.max(manufacturer_asTable)] 

 # dodge manufacturer has the most models 
 model_asTable <- table(mpg_file$model) 

 model_asTable 

 names(model_asTable)[which.max(model_asTable)]
 # caravan 2wd has the most variations
``` 

 2.a Group the manufacturers and find the unique models. Show your codes and result. 
```{r} 

manufacturers_models <- data.frame(Manufacturer = mpg_file$manufacturer, Model = mpg_file$model)
manufacturers_models

unique_mods <- unique(manufacturers_models)
unique_mods


```
 

2.b Graph the result by using plot() and ggplot(). Write the codes and its result
 
```{r} 

#install.packages("ggplot2")
library(ggplot2)

factoredManufacturer <- as.factor(unique_mods$Manufacturer)
manufacturerPlot <- plot(as.factor(factoredManufacturer),
                 main = "Unique Model per Manufacturer", 
                 cex.names = 0.8, las = 2)


#install.packages("dplyr")
library(dplyr)

unique_count <- unique_mods %>% 
  count(unique_mods$Manufacturer)
unique_count

names(unique_count) <- c("Manufacturer", "Number of Models")
unique_count

ggplot(unique_count, aes(x = Manufacturer, y = `Number of Models`)) +
geom_bar(stat = "identity")
``` 


2.  Same dataset will be used. You are going to show the relationship of the modeland the manufacturer.


2a.  What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?

```{r}
#This plot will display points representing the relationship between car models and their respective manufacturers. Each point would represent a unique combination of a car model and its manufacturer.
ggplot(mpg_file, aes(model, manufacturer)) + geom_point()


```

2b.  For you, is it useful? If not, how could you modify the data to make it more informative?

```{r}
#This visualization might not be very useful if there are many models or manufacturers, as the #points might overlap, making it hard to interpret. To improve this, you could aggregate the data to #show summary statistics per manufacturer or model. For instance, average fuel efficiency per #manufacturer or other aggregated metrics might provide more informative insights.
library(ggplot2)

model_manufacturer_count <- mpg %>%
  group_by(model, manufacturer) %>%
  summarise(count = n())

ggplot(model_manufacturer_count, aes(x = model, fill = manufacturer)) +
  geom_bar() +
  labs(title = "Number of Models per Manufacturer",
       x = "Model", y = "Count",
       fill = "Manufacturer") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

3.Plot the model and the year using ggplot(). Use only the top 20 observations. Write the codes and its results.

```{r}
library(ggplot2)


top_20 <- head(mpg_file, 20)


ggplot(top_20, aes(x = model, y = year)) +
  geom_point() +
  labs(title = "Top 20 Observations: Model vs. Year", x = "Model", y = "Year") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))  

```

4.Using the pipe (%\>%), group the model and get the number of cars per model. Show codes and its result.

```{r}

library(dplyr)


cars_per_model <- mpg_file %>%
count(model)  

```

4a.  Plot using geom_bar() using the top 20 observations only. The graphs shoudl have a title, labels and colors. Show code and results.

```{r}
library(ggplot2)

# Extracting the top 20 observations
top_20 <- head(mpg_file, 20)


ggplot(top_20, aes(x = model)) +
  geom_bar(fill = "skyblue", color = "black") +
  labs(title = "Number of Cars per Model (Top 20)", x = "Model", y = "Number of Cars") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) 
```

4b.  Plot using the geom_bar() + coord_flip() just like what is shown below. Show codes and its result.

```{r}

ggplot(cars_per_model, aes(x = model, y = n)) +
  geom_bar(stat = "identity", fill = "salmon", color = "black") +
  labs(title = "Number of Cars per Model", x = "Model", y = "Number of Cars") +
  coord_flip()


```

5.Plot the relationship between cyl - number of cylinders and displ - engine displacement using geom_point with aesthetic color = engine displacement. Title should be "Relationship between No. of Cylinders and Engine Displacement". a. How would you describe its relationship? Show the codes and its result.

```{r}
library(ggplot2)

# Plotting relationship between cyl and displ with color mapped to displ
ggplot(mpg_file, aes(x = cyl, y = displ, color = displ)) +
  geom_point() +
  labs(title = "Relationship between No. of Cylinders and Engine Displacement",
       x = "Number of Cylinders", y = "Engine Displacement") +
  scale_color_continuous(name = "Engine Displacement")  # Adding a color legend

```

6.Import the traffic.csv onto your R

```{r}
library(readr)
traffic <- read_csv("traffic.csv")

traffic

```

6a.  How many numbers of observation does it have? What are the variables of the traffic dataset the Show your answer.

```{r}
num_observations <- nrow(traffic)

num_variables <- ncol(traffic)


print(paste("Number of observations:", num_observations))
print(paste("Number of variables:", num_variables))


names(traffic)


```

6b.  subset the traffic dataset into junctions. What is the R codes and its output?

```{r}
unique_junctions <- unique(traffic$junctions)


junction_data <- lapply(unique_junctions, function(junction) {
  subset_data <- subset(traffic, junctions == junction)
  return(subset_data)
})

junction_data



```

6c.  Plot each junction in a using geom_line(). Show your solution and output.

```{r}
library(ggplot2)


plot_list <- lapply(junction_data, function(junction) {
  ggplot(junction, aes(x = time, y = traffic_volume)) + geom_line() + ggtitle("Traffic Volume")
})


plot_list 

```

7.  From alexa_file.xlsx, import it to your environment

```{r}
library(readxl)
alexa_file <- read_xlsx("alexa_file.xlsx")
alexa_file
```

a.  How many observations does alexa_file has? What about the number of columns? Show your solution and answer.

```{r}

nrow(alexa_file)
ncol(alexa_file)

```

7b.  group the variations and get the total of each variations. Use dplyr package. Show solution and answer.

```{r}
library(dplyr)

variation_totals <- alexa_file %>%
  group_by(variation) %>%
  summarise(total = n())

variation_totals

```

7c.  Plot the variations using the ggplot() function. What did you observe? Complete the details of the graph. Show solution and answer.

```{r}
library(ggplot2)

ggplot(alexa_file, aes(x = variation)) +
  geom_bar() +
  labs(title = "Distribution of Alexa Variations",
       x = "Variation",
       y = "Count") +
  theme_minimal()



```
