---
title: "Rworksheet_Esmalla#4b"
author: "Janessa Marie Esmalla"
date: "2023-11-08"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
#1 Using the for loop, create an R script that will display a 5x5 matrix as shown in Figure 1. It must contain vectorA = [1,2,3,4,5] and a 5 x 5 zero matrix.

vec_A <- c(1,2,3,4,5)
zero_matrix <- matrix(0,nrow=5,ncol=5)
matrix_result <- rbind(vec_A,zero_matrix)
print(matrix_result)
```

```{r}
#2 Print the string "*" using for() function. The output should be the same as shown in Figure


for(i in 1:5) {
  stars <- rep("*", i)
  print(stars)
}
```

```{r}
#3 Get an input from the user to print the Fibonacci sequence starting from the 1st input up to 500. Use repeat and break statements. Write the R Scripts and its output.

input <- as.integer(readline(prompt = "Enter a number: "))

prev <- 0
curr <- 1

print(curr)

repeat {
  next_num <- prev + curr
  if (next_num > 500) {
    break
  }
  print(next_num)
  prev <- curr
  curr <- next_num
}
```
```{r}
#4. Import the dataset as shown in Figure 1 you have created previously.







```{r}
#5 Create a piechart that will include labels in percentage.Add some colors and title of the chart. Write the R scripts and show its output.

incomespend_data <- data.frame(
  Category = c("Food", "Electricity", "Savings", "Miscellaneous"),
  Value = c(60, 10, 5, 25)
)

incomespend_data$Percentage <- incomespend_data$Value / sum(incomespend_data$Value) * 100

colors <- c("pink", "skyblue", "yellow", "violet")

pie(incomespend_data$Value,
    labels = paste(incomespend_data$Category, "(",incomespend_data$Percentage,"%)"),
    col = colors,
    main = "Monthly Income Spending of Dela Cruz Family")

legend("topright", incomespend_data$Category, fill = colors)
```


```{r}
#6. Use the iris dataset.

data(iris)



